---
title: "lmcoef"
output: html_vignette
vignette: >
  %\VigbetteIndexEntry{lmcoef tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lmcoef)
```

## lm_coef

Assume now we have a vector for the response variable, `y`, with length of n, and a n*m matrix for the independent variable `x`.

```{r}
y = c(78.5, 74.3, 104.3, 87.6, 95.9, 109.2, 102.7, 72.5, 93.1, 115.9, 83.8, 113.3, 109.4)
x = cbind(X1 = c(7, 1, 11, 11, 7, 11, 3, 1, 2, 21, 1, 11, 10), 
                     X2 = c(26, 29, 56, 31, 52, 55, 71, 31, 54, 47, 40, 66, 68), 
                     X3 = c(6, 15, 8, 8, 6, 9, 17, 22, 18, 4, 23, 9, 8), 
                     X4 = c(60, 52, 20, 47, 33, 22, 6, 44, 22, 26, 34, 12, 12))
data= cbind(y,x)
```

To use the function `lm_coef`:

```{r}
rst = lm_coef(y,x)
```

To compare the result for the estimated coefficients of this new implement with the original `lm` function:

```{r}
lm_est = summary(lm(y~., data))$coefficients
lm_coef_est = rst$coefficients

row.names(lm_est) <- NULL
colnames(lm_est) <- NULL

row.names(lm_coef_est) <- NULL
colnames(lm_coef_est) <- NULL

all.equal(lm_est, lm_coef_est)
```

Since 'anova' object must have colnames, To compare the result for the ANOVA table of this new implement with the original `lm` function, we just simply observe two outputs and they are the same:

```{r}
lm_anova = anova(lm(y~., data))
lm_coef_anova = rst$anova

lm_anova
lm_coef_anova
```

To compare the result for the residuals of this new implement with the original `lm` function:

```{r}
lm_res = as.vector(summary(lm(y~x))$residuals)
lm_coef_res = as.vector(rst$residuals)

all.equal(lm_res, lm_coef_res)
```

To compare the result for the residuals of this new implement with the original `lm` function:

```{r}
lm_fit = as.vector(summary(lm(y~x))$fitted.values)
lm_coef_fit = as.vector(rst$fitted.values)

all.equal(lm_res, lm_coef_res)
```

We compare the speed of these two implements - the new implement is slower than the original function:

```{r}
library(microbenchmark)
microbenchmark(summary(lm(y~x))$coefficients, lm_coef(y,x)$coefficients)
microbenchmark(anova(lm(y~x)), lm_coef(y,x)$anova)
microbenchmark(summary(lm(y~x))$residuals, lm_coef(y,x)$residuals)
microbenchmark(summary(lm(y~x))$fitted.values, lm_coef(y,x)$fitted.values)
```

## cpr_coef

`cpr_coef` is a integrated function that could achieve a single-step estimation of constraint polynomial regression. Currently, no fucntion like this has been included in any R package. The conventional implementation was based on the `lm` function and needed prior calculation before finally using `lm`. This new implementation would save much time when user facing a condition as the following example.

As an example, assume now we know we would like to fit a polynomial regression with the power (`p`) of 3, and we have a group of outcome data `y`, that is:

```{r}
p = 3
y = c(0.5 ,1 ,1.5)
```

For each `y`, if the following constraint is proposed for the given model:

for $i = 1,2,...,n$ and $\epsilon_i \sim N(0,\sigma^2)$, 

$$Y_i = \beta_0 + \sum_{j=1}^p{\beta_j * (X_i) ^ j} + \epsilon_i$$ 

where coefficient $\beta_j = \beta_{j-1} / j$ for $j = 2,...,p$, and predictor $X_i = i / n$,

the function `cpr_coef` could be implemented:

```{r}
rst = cpr_coef(p,y)
```

To compare the result for the estimated coefficients of this new implement with the original `lm` function:

```{r}
# Using lm function
lm_res <- function(p, y){
  n = length(y)
  x = (1:n) / n
  x_final = x / p
  ## apply Horner's rule to compute polynomial ##
  if(p > 1){
    for(j in seq(p-1, 1, by = -1)){
      x_final = x_final + 1
      x_final = x / j * x_final
    }
  }
  b1 = summary(lm(y ~ x_final))$coefficients[2,1]
  b0 = summary(lm(y ~ x_final))$coefficients[1,1]
  beta_n = c(b1)
  for (k in 1:(p-1)){
    beta_n = append(beta_n, beta_n[k] / (k+1))
  }
  beta = c(b0, beta_n)
  return(beta)
}

lm_est = lm_res(p,y)
cpr_coef_est = as.vector(cpr_coef(p,y)$coefficients)

row.names(cpr_coef_est) <- NULL
colnames(cpr_coef_est) <- NULL

all.equal(lm_est, cpr_coef_est)
```

By comparing the speed of these two implements, we could observe that the `cpr_coef` function could save much time: 

```{r}
library(microbenchmark)
microbenchmark(lm_res(p,y), cpr_coef(p,y)$coefficients)
```
